---
title: "JGCRI Colors User Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette_examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```


<style type="text/css">
.column-left{
  float: left;
  width: 50%;
}
.column-right{
  float: right;
  width: 50%;
}
.clearer {clear: both}
</style>

<!-------------------------->
<!-------------------------->
# Key Links
<!-------------------------->
<!-------------------------->

- Github: https://github.com/JGCRI/jgcricolors
- Webpage: https://jgcri.github.io/jgcricolors
- R Colors: http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf?utm_source=twitterfeed&utm_medium=twitter
- R Color Palette Cheatsheet: https://www.nceas.ucsb.edu/sites/default/files/2020-04/colorPaletteCheatsheet.pdf 
- HEX Colors: https://htmlcolorcodes.com/

<!-------------------------->
<!-------------------------->
# Available Palettes
<!-------------------------->
<!-------------------------->

```{r, eval=TRUE, warning=FALSE, message=FALSE}
library(jgcricolors)

# See all available color palettes
names(jgcricol())

# Load a color palette
mypal1 <- jgcricol()$pal_basic  # To load values only
mypal2 <- jgcricol("pal_basic") # To see an example piechart and values

```


<!-------------------------->
<!-------------------------->
# JGCRI Colors (pal_all)
<!-------------------------->
<!-------------------------->

`jgcricol("pal_all")` is a comprehensive color palette which applies to most JGCRI and GCAM outputs. These can be used for line and bar charts. The following code shows how you can use the same `pal_all` for various bar charts in ggplot. 

```{r, eval=F, echo=T, warning=FALSE, message=FALSE}
library(jgcricolors)
library(ggplot2)

# Set your palette
mypal = jgcricol()$pal_all

# Example categories for data to plot 
# Can replace these with any other GCAM technologies or classes as done in the subsequent figures.
techs = c("a oil","a oil CCS","b natural gas","b natural gas CCS","c coal","c coal CCS",
    "d biomass","d biomass CCS","e nuclear","f hydro","g wind","h solar","i geothermal",
    "j traditional biomass","energy reduction")

# Create data
data <- data.frame(label=rep(techs,each=4), x=rep(c(1:4),length(techs)), value=runif(4*length(techs)))

# Plot
  print(ggplot(data, aes(x=x,y=value, fill=label)) +
      geom_bar(position="stack", stat="identity", col="black",lwd=0.5) +
      scale_fill_manual(values=mypal) +
      theme_bw() +
      xlab(NULL) + 
      ylab(NULL) + 
      ggtitle("Primary Energy"))

```

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
library(jgcricolors)
library(ggplot2)

# Set your palette
mypal = jgcricol()$pal_all

# Example lists of different GCAM data
listx <- list(
  # Primary energy colors including CCS
  `Primary energy` = c(
    "a oil","a oil CCS","b natural gas","b natural gas CCS","c coal","c coal CCS",
    "d biomass","d biomass CCS","e nuclear","f hydro","g wind","h solar","i geothermal",
    "j traditional biomass","energy reduction"),
  
  `Elec gen by fuel` = c( "a Coal",
      "b Coal w/CCS",
      "c Gas",
      "d Gas w/CCS",
      "e Oil",
      "f Oil w/CCS",
      "g Biomass",
      "h Biomass w/CCS",
      "i Nuclear",
      "j Geothermal",
      "k Hydro",
      "l Wind",
      "m Solar",
      "n CHP",
      "o Battery",
      "energy reduction"),
  
  `Elec by Tech` = c('biomass',
      'coal',
      'gas',
      'geothermal',
      'grid_storage',
      'hydro',
      'hydrogen',
      'nuclear',
      'refined liquids',
      'rooftop_pv',
      'solar',
      'wind'),
  
  `Transport by fuel` = c( "liquids",
      "gas",
      "coal",
      "biomass",
      "electricity",
      "hydrogen"),
  
  `Transport by tech` = c( 
    "LDV",
    "Bus",
    "Rail",
    "Plane",
    "MotorBike",
    "Truck",
    "Ship",
    "2W", 
    "3W", 
    "LHDT", 
    "MHDT", 
    "HHDT"),
  
    `AgLu by crop` = c( 'Biomass',
      'Corn',
      'FiberCrop',
      'Fodder',
      'Forest',
      'Grass',
      'MiscCrop',
      'OilCrop',
      'Other',
      'PalmFruit',
      'Pasture',
      'Rice',
      'RootTuber',
      'Shrub',
      'SugarCrop',
      'Urban',
      'Wheat'),
  
    `Water by sec` = c( 'agriculture',
      'electricity',
      'industry',
      'livestock',
      'mining',
      'municipal'
      )
  
    )
              
for(i in 1:length(listx)){
  techs = listx[[i]]              
  data <- data.frame(label=rep(techs,each=4), x=rep(c(1:4),length(techs)), value=runif(4*length(techs)))
  cat("  \n##", names(listx[i]), "  \n")
  print(ggplot(data, aes(x=x,y=value, fill=label)) +
    geom_bar(position="stack", stat="identity",col="black",lwd=0.5) +
    scale_fill_manual(values=mypal) +
    theme_bw() +
    xlab(NULL) + ylab(NULL))
  cat('<div class="clearer"></div>')
}

```

<!-------------------------->
<!-------------------------->
# Add Missing Colors
<!-------------------------->
<!-------------------------->

Users can add a color to any jgcricolor palette which may be missing by adding a color from the available [R colors](http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf?utm_source=twitterfeed&utm_medium=twitter) of any [HEX color](https://htmlcolorcodes.com) and assigning it a name. For example if a user wants to add two new colors for `animal energy` with the color `human` and for `animal energy` with the HEX color `#FFF700` they can do so as follows.

```{r, eval=T, warning=FALSE, message=FALSE}
library(jgcricolors)
library(graphics)
mypal1 <- jgcricol()$pal_basic  # To load silently
names(mypal1) <- mypal1
mypal2 = c(mypal1,"animal energy"="#FFF700", "human energy"="lawngreen")
par(mfrow=c(1,2))
par(mai = c(0.5, 0.5, 0.5, 0.5))
pie(rep(1,length(mypal2)),label=names(mypal1),col=mypal1, main="Pal 1 w/ Missing Colors") # Plot as pie chart
pie(rep(1,length(mypal2)),label=names(mypal2),col=mypal2, main="Pal 2 w/ Added Colors") # Plot as pie chart
```

<!-------------------------->
# Other Palettes
<!-------------------------->

```{r, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE,results = 'asis'}
library(jgcricolors)
library(ggplot2)

# See all available color palettes
my_pals <- names(jgcricol())[!names(jgcricol()) %in% c("pal_all","pal_sankey")]
 
for(i in my_pals){
  mypal <- jgcricol()[[i]]
  if(i != "pal_scarcityCat"){names(mypal) <- mypal}
  mypal1 <- mypal
  names(mypal1) <- NULL
  cat("  \n##",  i, "  \n")
  cat('<div class="column-left">')
  par(mai = c(0, 0, 0, 0))
  pie(rep(1,length(mypal)),label=names(mypal),col=mypal)
  cat('</div>')
  cat('<div class="column-right">')
  cat('<p></p>')
  cat('<p></p>')

  print(ggplot() +
  geom_polygon(data =  jgcricolors::mapUS49df,
               aes(x = long, y = lat, group = group, fill = subRegion),
               colour = "gray10", lwd=0.5) +
  scale_fill_manual(values=rep(mypal1,50)[1:length(unique(jgcricolors::mapUS49df$subRegion))]) +
  theme_void() +
  coord_fixed(ratio = 1.25) +
  theme(legend.position = "none"))

  cat('</div>')
  cat('<div class="clearer"></div>')
}
```

<!-------------------------->
# Create custom ramped pallete
<!-------------------------->
Users can create their own ramped palettes of any length `n` using the `RcolorBrewer` package and choosing an R palette from the [R color palette cheatsheet](https://www.nceas.ucsb.edu/sites/default/files/2020-04/colorPaletteCheatsheet.pdf). 

```{r, eval=TRUE, warning=FALSE, message=FALSE}
library(RColorBrewer)
library(graphics)
getcol = colorRampPalette(brewer.pal(9, 'Pastel1')); 
values=getcol(9);
pie(rep(1,length(values)),label=names(values),col=values)
```

